% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}} 

\usepackage{graphicx}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{url}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em 
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
% Put edit comments in a really ugly standout display
\usepackage{times}
 
% Macros for proof-reading & corrections
\usepackage[normalem]{ulem} % for \sout  
\usepackage{xcolor} 

% Macros for proof-reading & corrections
\usepackage[normalem]{ulem} % for \sout  
\usepackage{xcolor} 

\usepackage{ifthen}
\usepackage{amssymb} 
\newboolean{showcomments}  
\setboolean{showcomments}{true} % toggle to show or hide comments
\ifthenelse{\boolean{showcomments}}     
  {\newcommand{\nb}[2]{
    \fcolorbox{gray}{yellow}{\bfseries\sffamily\scriptsize#1}
    {$\blacktriangleright$#2$\blacktriangleleft$}
   }
   \newcommand{\version}{\emph{\scriptsize$-$working$-$}} 
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\version}{} 
  } 

\newcommand\levi[1]{\nb{Levi}{\textcolor{teal}{#1}}}
\newcommand\andreas[1]{\nb{Andreas}{\textcolor{teal}{#1}}}
\newcommand\sk[1]{\nb{sk}{\textcolor{teal}{#1}}}

\newcommand{\af}{\textsc{AF3}\xspace}
\newcommand{\autofocus}{\textsc{AutoFOCUS3}\xspace}

\newcommand{\ears}{\textsc{Ears}\xspace} 
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\earsctrl}{\textsc{Ears-Ctrl}\xspace}
\newcommand{\ltl}{\textsc{Ltl}\xspace}
\newcommand{\iets}{\textsc{Iets3}\xspace}
\newcommand{\fig}{\text{Figure}\xspace}
\newcommand{\sect}{\text{section}\xspace} 
\newcommand{\tab}{\text{table}\xspace}
\newcommand{\eg}{\text{e.g.}\xspace}
\newcommand{\pid}{\textsc{Pid}\xspace}
\newcommand{\clang}{\textsc{C}\xspace}
\newcommand{\java}{\textsc{Java}\xspace}
\newcommand{\ecu}{\textsc{Ecu}\xspace}
\newcommand{\acc}{\textsc{Acc}\xspace} 

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document} 
% 
\title{Controlling a Virtual Rover using AutoFOCUS3}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Levi L\'ucio \and
Sudeep Kanav \and Andreas Bayha \and Johannes Eder} 
%
%\authorrunning{Levi L\'ucioSudeep Kanaav}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{fortiss GmbH\\ Guerickestra\ss e 25\\80805 M\"unchen\\
\email{\{lucio,kanav,bayha,eder\}@fortiss.org}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\autofocus (\af) is a mature model-driven engineering environment for developing
software for embedded systems. For the past 20 years, several versions of \af
have served as a platform for experimenting with cutting edge research ideas in
Model-Driven Development.
\af is a tool that fully encompasses the software lifecycle, from requirements,
to architecture, simulation, deployment, code generation and verification. In
this article we describe how we used an existing model of a complex controller
for a real-life miniature vehicle and have downsized and adapted it to control a rover in a
virtual environment. The model we present here automates the maneuvering
of a rover to follow another leader rover in a virtual environment, while
keeping a safe distance to it. The controller operates by adapting the rover's
speed and steering according to the position and movements of the leader.
The results we present in this article illustrate the whole development cycle of
an embedded system using \af, from the development of the model down to
deployment to a specific platform as well as code generation and connecting to
the hardware. 
 
\keywords{Modelling Environment \and Embedded Systems \and Deployment \and Code
Generation \and Controller.}
\end{abstract}
  
\input{text/introduction}

\input{text/physical_rover_model}

%\input{text/reduced_model}  
 
\input{text/reduced_model_new}
 
\input{text/code_generation}

\input{text/conclusion} 

\bibliographystyle{abbrv} 
\bibliography{./references}

\end{document}
